### 2025-01-28 paper/icml25/first/sects/introduction.tex
stronger statement on the contribution (@f14-bertolotti check)

We summarize our contributions as follows:
\begin{compactitem}
    \item We propose a new reinforcement learning framework that lift the requirement for a differentiable simulator in SHAC\@.
    \item We assess the SHAC algorithm in multi-agent scenarios, where it has not been previously evaluated.
    \item We evaluate our algorithm against PPO and SHAC on a set of environments with increasing numbers of agents.
    \item We show that our algorithm achieve SHAC-like performance in differentiable environments and outperform PPO in non-differentiable environments.
\end{compactitem}

>>>>

We summarize our contributions as follows:
\begin{compactitem}
    \item We propose a new reinforcement learning framework that lifts the requirement for a differentiable simulator in SHAC\@.
    \item We assess the SHAC algorithm in multi-agent scenarios, where it has not been previously evaluated.
    \item We evaluate our algorithm against PPO and SHAC on a set of environments with increasing numbers of agents.
    \item We demonstrate that our algorithm matches SHAC's performance in differentiable environments while significantly outperforming PPO in terms of sample efficiency, convergence speed, and final reward across both single-agent and complex multi-agent scenarios.
\end{compactitem}
